---
title: "PeerGroup2_PeerCommentary_ishratc_01"
author: "Ishrat Chowdhury"
date: "September 15, 2019"
output: html_document
---

---
title: "ishratc_OriginalHomeworkCode_01"
author: "Ishrat Chowdhury"
date: "September 11, 2019"
output: html_document
---

#Homework 1

Matrix, Arrays, and Vector Practice

```{r}
m <- matrix(data=c(1,2,3,4,5,6),nrow=2,ncol=3,byrow=TRUE)
m

v1 <- c(1,2,3,4)
v2 <- c(6,7,8,9)
m1 <- rbind(v1,v2)
m1

m2 <- cbind(v1,v2)
m2

v <- 101:200
v[seq(from = 1, to = 50, by = 2)]

```

##CHALLENGE 1

vector of 1 word character strings ...

```{r}

v1<-c("Stately,","plump","Buck","Mulligan","came","from","the","stairhead,","bearing","a","bowl","of","lather","on","which","a","mirror","and","a","razor","lay","crossed.")
v1
l<-length(v1)
l?
```
#peer comment: attempts to extract every third  use teh function seq().

not sure how to do this with the str_split() function,
#peer comment:check by ?stringr::str_split on how to use thsi function.

#peer comment:change the vector to make it one sentence, and then get rid of the punctuation



```{r}
x<- v1[c(1,4,7,10,13,16,19,22)]
x
```

##CHALLENGE 2

```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m
```

extract columns 2, 3 and 6 and assign to varibale x

```{r}
x<-c(m[,2], m[,3], m[,6])
x

```

extract row 6 and row 8 and assign to variable x 

```{r}
x<-c(m[6,], m[8,])
x
```

extract elements from row 2, column 2 to row 6, column 9 and assign them to the variable x

```{r}
x<-c(m[2:6, 2:9])
x
```

##CHALLENGE 3

Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)

```{r}
a <- array(data=400:1, dim=c(5,5,4,4))
a
```

Given this matrix, what would the following return?

```{r}
a[1, 1, 1, 2]

```
the element in table 1,2 at row 1 column 1


```{r}
a[2, 3, 2, ]

```

the elements in column row 2 column 3 of every "2nd"" table 
is there a better way to verbalize what it is selecting?

```{r}
a[1:5, 1:5, 3, 3]

```

print rows 1-5 and columns 1-5 for table 3,3. this is basically a copy of table 3,3.
#peer comment: instead of using code, just give the answer
Practice overwriting

```{r}
m[7,1] <- 564
m
```

replaces row 7 column 1 with new value

```{r}
m[,8] <- 2
m
```

replaces column 8 with value 2, changesx made before are still present

```{r}
m[2:5,4:8] <- 1
m
```

replace row 2-4 and column 5 -8 with 1. overwrites previous commands. 

```{r}
m[2:5,4:8] <- c(20,19,18,17)
m
```

replaces each row with new value while overwriting 

```{r}
m[2:5,4:8] <- matrix(data = c(20:1), nrow=4,ncol=5,byrow=TRUE)
m
```

a new matrix was embedded within this matrix

```{r}
m[,8] <- c("a","b")
m
```

column 8 gets replaced with a and b but now everything is a character 

Lists and Data Frames Practice 

```{r}
s <- c("this","is","a","vector","of","strings")
m <- matrix(data=1:40, nrow=5, ncol=8) # this is a matrix
b <- FALSE
l <- list(s, m, b)
l
l[[2]]
```

##CHALLENGE 4

not sure if I should start with conactonating or list to begin with

```{r}
Platyrrhini<- list("Cebidae","Atelidae","Pitheciidae")
Catarrhini<- list("Cercopithecidae","Hylobatidae","Hominidae")
Haplorini<- list(Platyrrhini, Catarrhini)
Tarsioidea<- list("Tarsiidae")
Lorisoidea<- list("Lorisidae", "Galagidae")
Lemuroidea<- list("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Strepsirhini<- list(Lorisoidea, Lemuroidea)
Primates<- list(Haplorini, Strepsirhini)
Primates

```


```{r}
Platyrrhini<- c("Cebidae","Atelidae","Pitheciidae")
Catarrhini<- c("Cercopithecidae","Hylobatidae","Hominidae")
Haplorini<- list(Platyrrhini, Catarrhini)
Tarsioidea<- c("Tarsiidae")
Lorisoidea<- c("Lorisidae", "Galagidae")
Lemuroidea<- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Strepsirhini<- list(Lorisoidea, Lemuroidea)
Primates<- list(Haplorini, Strepsirhini)
Primates
```
#peer comment:do the names()to name each list.
I think concatonating at first looks better but I would like to clean this up more
need help making this more presentable

Data frame practice 

```{r}
df <- read.csv("C:/Users/Ishrat/Documents/AN597-Week2/random_people", sep =",", header = TRUE, stringsAsFactors = FALSE)
# only print select columns
df[,c(1,3,4,11,12)]
str(df)
df[,3]
```

##CHALLENGE 5

create matrix

```{r}
w<-matrix(c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol =  3, byrow = TRUE)
w
```

coerce it as a data frame

```{r}
wdf<- as.data.frame(w)
wdf
```

coerce the second column to be logical-valued
coerce the third column to be factor-valued

```{r}
wdf[,2] = as.logical(2)
wdf[,3] = as.factor(3)
str(wdf)
```


##Problems to discuss for peer comentrary

-need help using str_split() function
-I can see what's happening in the 4D array but can we discuss what exactly is the differenct betweent the third and fourth dimmensions
-I tried both lsiting and conncatonating the phylogeny however any tips to clean this up some more, I'm nto sure if this is the way it should look


